### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Constraint Solving}
As discussed in \S\ref{side-channel:condition}, the problem of identifying
side-channels can be reduced to the question below.

@@

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model.

Moreover, for some crypto library, we evaluate more than one versions. After that, we compare the evaluation results with the version history to track developers' patches of those leakages.
\begin{itemize}
  \item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
  \item MbedTLS: 2.5, 2.15
  \item Libgcrypt: 1.8.5
  \item Monocyper: 3.0
\end{itemize}

We mark variables and buffers that store a secret.
For DES and AES, we mark symmetric keys as secrets.
For RSA, we mark private keys as secrets. For ECDSA,
we mark nonces and private keys as secrets.

We build the source program into 32-bit x86 Linux executables with GCC 7.5
running on Ubuntu 16.04.
We run our experiments on a 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB
RAM. The execution time is calculated on a single-core.

@@

  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks),

@@

    The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.

@@

  \newlength{\x}
  \newlength{\y}
  \settowidth{\x}{~~}
  \settowidth{\y}{m}
  \addtolength{\x}{-1\y}
  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}

@@

@@

    Total              &                          & 904               & 241               & 663            & 167,141,947 & 341m            \\\hline
  \end{tabular}
\end{table*}
Table~\ref{table:over_result} summarizes the results.
\tool{} finds 904 leaks in the crypto libraries.
Among these 904 leaks, 241 are due to secret-dependent
control-flow transfers and 663 are due to secret-dependent data accesses.

@@

We also evaluate our tool on the RSA implementation. With the optimization
introduced in \S\ref{sec:scala}, we need not apply domain knowledge to
simplify the analysis. Our tool identifies all leakage sites
reported by CacheD~\cite{203878} and find new leaks in less time.
We also find newer
versions of RSA in OpenSSL have fewer leaks. We
will discuss the version changes and corresponding leakages in \S\ref{eval:asym}.

@@

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While those optimizations do not introduce false positives, they may miss some
vulnerabilities.
We notice that the number of instructions in those traces are different due to the different analysis starting
functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\tool{} on AES from OpenSSL
0.9.7, \tool{} is over 100x faster than CacheD.
\begin{table}[]
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}
  \begin{threeparttable}
    \begin{tabular}{@{}c|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
      Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
      AES\tnote{1}          & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
      AES\tnote{2}          & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
      RSA\tnote{1}          & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
      RSA\tnote{2}          & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
      RSA\tnote{3}          & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
      RSA\tnote{4}          & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
    \end{tabular}
  \end{threeparttable}
  \begin{tablenotes}
    \scriptsize
    \item[1] OpenSSL\,0.9.7  \item[2] OpenSSL\,1.0.2f   \item[3] Libgcrypt\,1.6.1 \item[4] Libgcrypt\,1.7.3 \\
  \end{tablenotes}
  \vspace*{-20pt}
\end{table}
Since DATA~\cite{217537} needs to compare several execution
traces to identify side-channel leakages, \tool{} also outperforms
DATA in terms of performance. For
example, it takes 234 minutes for DATA to analyze the RSA of
implementation in OpenSSL 1.1.0f. \tool{} only spends 34 minutes
according to Table~\ref{table:over_result}.  Also, DATA reports
report 278 control-flow and 460 memory-access leaks. Among those
leakages, they find one new vulnerability in RSA after some manual
analysis.  \tool{} finds the vulnerability and reports the
vulnerability is severe (\textsf{int\_bn\_mod\_inverse} leaks more
than 14.9 bits and \textsf{BN\_div} leaks more than 17.2 bits),
which eases the pain to identify real sensitive leaks.}{DATA~\cite{217537} identifies
side-channel leakages by finding differences in execution traces of
the test program under \emph{various secret inputs}. According to
the original DATA paper, it uses 443 different traces to analyze the
side-channel vulnerabilities in symmetric cyphers and 450 different
traces to analyze the side-channel vulnerabilities in asymmetric
cyphers. On the other hand, \tool{} detects side-channel
vulnerabilities from one execution trace. \tool{} uses symbolic
analysis to extract formulas that model each side-channel
leakage. After that, we sample the formula with \emph{various
  secret inputs} to detect and quantify each leakage site. In
theory, DATA might have better code coverage than \tool{} because it
uses more execution traces,  but \tool{} has the following
advantages. a) \tool{} is faster than DATA. For example, it takes
116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@. \tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}. It takes 13 minutes and 20 minutes
for DATA to analyze the side-channel leakages in AES and DES,
respectively. On the other hand, \tool{} finishes its analysis in
less than ten seconds while finding all the leakages reported by
DATA. b) Because \tool{} does not run the test program again when we
have a new \emph{secret input}, \tool{} can test more input secrets
on those formulas within the same time to achieve better precision.
c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
The strength of Abacus is that it does not need such domain knowledge.
DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
\tool{} finds the vulnerability and reports the vulnerability is
severe (\textsf{int\_bn\_mod\_inverse} leaks more than 14.9 bits and
\textsf{BN\_div} leaks more than 17.2 bits), which helps identify
real sensitive leaks.  For each leakage site, \tool{} can provide
concrete examples to trigger the issue and give an estimation to
assess the severity level of the vulnerability.
\section{Discussion}

>>>>

\subsection{Constraint Solving}
As discussed in the previous section, the problem of identifying
side-channels can be reduced to the question below.

@@

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a crytpographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.

For some crypto libraries, we evaluate multiple versions. After that, we compare the evaluation results with the version history to track those leakages' patches. In summary, we evaluate our tool on the following libraries.
\begin{itemize}
  \item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
  \item MbedTLS: 2.5, 2.15
  \item Libgcrypt: 1.6.1, 1.7.3, 1.8.5
  \item Monocyper: 3.0
\end{itemize}

We refer to the examples or test cases of those libraries and write simple
programs that use the crypto libraries. For symmetric encryption, the length
of the keys are 256 bit. For RSA, the length of the keys is 1024. For ECDSA, the
length of the key is 384 bit. The input public message is ``Hello World!''.
We mark variables and buffers that store a secret.
For DES and AES, we mark symmetric keys as secrets.
For RSA, we mark private keys as secrets. For ECDSA,
we mark nonces and private keys as secrets.

We build the source program into 32-bit x86 Linux executables with GCC 7.5
running on Ubuntu 16.04. While our tool can work on the stripped binaries, 
in the evaluation, we keep the debug information to get the fine-grained infromation
(e.g., line numbers).
We run our experiments on a 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB
RAM. We run the experiments simultaneously, but the execution time is calculated on a single-core.

@@

  \caption{Evaluation results overview: Algorithm, Implementation, Side-channel Leaks\,(Leaks),

@@

    The number of instructions\,(\# Instructions), The Execution Time, and The Memory Usage.

@@

@@

    Triple DES         & OpenSSL 1.1.0f &  9 &0  &9   &13,105   & 369 & 56\\

@@

    Total              &                          & 913               & 241               & 672            & 167,155,052 & 341m            \\\hline
  \end{tabular}
\end{table*}
Table~\ref{table:over_result} summarizes the results.
\tool{} finds 913 leaks in the crypto libraries.
Among these 913 leaks, 241 are due to secret-dependent
control-flow transfers and 672 are due to secret-dependent data accesses.

@@

We also evaluate our tool on the RSA implementation. With the optimization
introduced in the previous sections, we need not apply domain knowledge to
simplify the analysis. Our tool identifies all leakage sites
reported by CacheD~\cite{203878} and find new leaks in less time.
We also find newer
versions of RSA in OpenSSL have fewer leaks.

@@

The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
Note that one statement in the source code can be compiled into several machine instructions. So it is possible that one statement can have multiple leakage points. Under the circumstance, we think it is only a leakage.
We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
CacheD fails to detect some vulnerabilities for two
reasons. First, CacheD can only detect secret-dependent data access
vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
Second, according to the CacheD paper, CacheD times out after 20 hours to process
asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
the analysis.
While those optimizations do not introduce false positives, they may miss some
vulnerabilities.
We notice that the number of instructions in those traces are different due to the different analysis starting
functions and building options during the evaluation.
Table~\ref{eval:cacheD} shows that
\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
number of instructions. For example, when we test~\tool{} on AES from OpenSSL
0.9.7, \tool{} is over 100x faster than CacheD.
\begin{table*}[]
 \centering
  \caption{Comparison with CacheD: Time,
    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
  \label{eval:cacheD}

    \begin{tabular}{@{}c|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
      \hline
      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
      Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
      AES\tnote{1}          & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
      AES\tnote{2}          & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
      RSA\tnote{1}          & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
      RSA\tnote{2}          & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
      RSA\tnote{3}          & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
      RSA\tnote{4}          & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
    \end{tabular}

\end{table*}
DATA~\cite{217537} identifies
side-channel leakages by finding differences in execution traces of
the test program under \emph{various secret inputs}. According to
the original DATA paper, it uses 443 different traces to analyze the
side-channel vulnerabilities in symmetric cyphers and 450 different
traces to analyze the side-channel vulnerabilities in asymmetric
cyphers. On the other hand, \tool{} detects side-channel
vulnerabilities from one execution trace. \tool{} uses symbolic
analysis to extract formulas that model each side-channel
leakage. After that, we sample the formula with \emph{various
  secret inputs} to detect and quantify each leakage site. In
theory, DATA might have better code coverage than \tool{} because it
uses more execution traces,  but \tool{} has the following
advantages. a) \tool{} is faster than DATA. For example, it takes
116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@. \tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}. It takes 13 minutes and 20 minutes
for DATA to analyze the side-channel leakages in AES and DES,
respectively. On the other hand, \tool{} finishes its analysis in
less than ten seconds while finding all the leakages reported by
DATA. b) Because \tool{} does not run the test program again when we
have a new \emph{secret input}, \tool{} can test more input secrets
on those formulas within the same time to achieve better precision.
c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
The strength of Abacus is that it does not need such domain knowledge.
DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
\tool{} finds the vulnerability and reports the vulnerability is
severe (\textsf{int\_bn\_mod\_inverse} leaks more than 14.9 bits and
\textsf{BN\_div} leaks more than 17.2 bits), which helps identify
real sensitive leaks.  For each leakage site, \tool{} can provide
concrete examples to trigger the issue and give an estimation to
assess the severity level of the vulnerability.
\section{Discussion and Limitation}
